Lineage Analysis of CRISPR and shRNA Screens

### 2018-10-19 18Q3.Rmd
renamed and rearranged for manuscript.Rmd

## Make drug screen boxplots
```{r}
makeDrugBoxplots <- function(drug, dataset) {
  if(dataset == "CCLE" | dataset == "ccle") {
    use_data <- filter(ccle_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ccle_signif_lvlA_ByDrug[[drug]]
    # sig <- filter(ccle_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else if(dataset == "CTRP" | dataset == "ctrp") {
    use_data <- filter(ctrp_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ctrp_signif_lvlA_ByDrug[[drug]]
    # sig <- filter(ctrp_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else if(dataset == "GDSC" | dataset == "gdsc") {
    use_data <- filter(gdsc_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- gdsc_signif_lvlA_ByDrug[[drug]]
    # sig <- filter(gdsc_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else { return("Error: Invalid dataset.") }

>>>>

## Make drug screen boxplots

```{r}
makeDrugBoxplots <- function(drug, dataset) {
  if(dataset == "CCLE" | dataset == "ccle") {
    use_data <- filter(ccle_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ccle_signif_lvlA_ByDrug[[drug]]
    # sig <- filter(ccle_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else if(dataset == "CTRP" | dataset == "ctrp") {
    use_data <- filter(ctrp_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ctrp_signif_lvlA_ByDrug[[drug]]
    # sig <- filter(ctrp_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else if(dataset == "GDSC" | dataset == "gdsc") {
    use_data <- filter(gdsc_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- gdsc_signif_lvlA_ByDrug[[drug]]
    # sig <- filter(gdsc_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else { return("Error: Invalid dataset.") }
